DeepSphere: a graph-based spherical CNN

### 2020-02-14 main.tex
acknowledge software

We thank Pierre Vandergheynst for advices.
%and Andreas Loukas for having processed the GHCN data.
We thank Taco Cohen for his inputs on the intriguing results of our comparison with \citet{cohen2019gauge}.
We thank the anonymous reviewers for their constructive feedback.
%The following software packages were used for computation and plotting: pygsp, scipy, numpy, tensorflow, etc.
%We used the Python Graph Signal Processing package (PyGSP) \citep{pygsp} for computations and plots.

>>>>

We thank Pierre Vandergheynst for advices,
%and Andreas Loukas for having processed the GHCN data.
and Taco Cohen for his inputs on the intriguing results of our comparison with \citet{cohen2019gauge}.
We thank the anonymous reviewers for their constructive feedback.
The following software packages were used for computation and plotting: PyGSP \citep{pygsp}, healpy \citep{healpy}, matplotlib \citep{matplotlib}, SciPy \citep{scipy}, NumPy \citep{numpy}, TensorFlow \citep{tensorflow}.
%We used the Python Graph Signal Processing package (PyGSP) \citep{pygsp} for computations and plots.
